\emph{icepack}: a novel glacier flow modeling package

### 2019-08-16 icepack.tex
Added citation to Langdon and Raymond 1978

The shallow ice and shallow stream models in icepack are completely standard.
The hybrid flow model that we describe here is based on variational principles, terrain-following coordinates, and vertical spectral methods.
Each of these methods has appeared in the literature on glacier modeling before but never all in the same place for a 3D model.
\citet{bassis2010hamilton} \textcolor{red}{and Charlie} used variational principles and vertical spectral methods, but these works considered only flowband and not 3D models.
\citet{kleiner2014numerical} used terrain-following coordinates for 3D glacier flow modeling, but they discretized the problem with finite difference methods in every direction and did not take into account the variational formulation of the diagnostic model.
\citet{jouvet2015multilayer} used vertical semi-discretization of the variational problem, but this model used a finite difference discretization in the vertical direction.

>>>>

The shallow ice and shallow stream models in icepack are completely standard.
The hybrid flow model that we describe here is based on variational principles, terrain-following coordinates, and vertical spectral methods.
Each of these methods has appeared in the literature on glacier modeling before but never all in the same place for a 3D model.
\citet{langdon1978numerical} and \cite{bassis2010hamilton} used variational principles and vertical spectral methods, but these works considered only flowband and not 3D models.
\citet{kleiner2014numerical} used terrain-following coordinates for 3D glacier flow modeling, but they discretized the problem with finite difference methods in every direction and did not take into account the variational formulation of the diagnostic model.
\citet{jouvet2015multilayer} used vertical semi-discretization of the variational problem, but this model used a finite difference discretization in the vertical direction.
